A free/open-source machine translation system for English to Kazakh

### 2015-03-07 engkaz-eamt-2015/engkaz-eamt-2015.tex
delete revision at 3.2
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59248 72bbbca6-d526-0410-a7d9-f06f51895060

This section describes the current structural transfer in \texttt{apertium-eng-kaz} (revision 58998, ).\todo{Complete! 58998? Move to results?} English--Kazakh 
chunker rules, interchunk rules and an additional clean-up stage will be described in detail in the following 3 sections.

>>>>

This section describes the current structural transfer in \texttt{apertium-eng-kaz}.\todo{Complete! 58998? Move to results? - moved} English--Kazakh 
chunker rules, interchunk rules and an additional clean-up stage will be described in detail in the following 3 sections.
